Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-03-13 manuscript/supplementaryRW.Rmd
added the env gradient with same y axis

---
title: "Supplementary figures\nCapturing regeneration in models of forest dynamics"
author: 
- Olalla Díaz-Yáñez, 
- Yannek Käber, 
- Mats Mahnken, 
- Samuel Fischer, 
- Xavier Morin, 
- Manfred Lexer, 
- Christian Hochauer, 
- Katarina Merganicova, 
- Tobias Mette, 
- Werner Rammer, 
- Kristin H. Braziunas, 
- Paola Mairota, 
- Josef Bruna,
- Heike Lischke, 
- Daniel Scherrer, 
- Simon Scheiter, 
- Thomas Hickler, 
- Tim Anders,
- Jessica Hetzer, 
- Harald Bugmann
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: global-change-biology.csl
editor_options: 
  markdown: 
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

```{r nvTrend710BAlightTemp, echo=FALSE, fig.cap="Mean ingrowth values across the 200 samples per site, for the 200 sites against gradients of (a) total basal area; (b) climatic water balance; (c) seasonal degree sum. The values were split into ten bins; the red lines represent a GAM model showing the trend in the observed data. The same graphs with y-axis scaled by model as availalbe in Figure S", fig.show = 'hold', out.width="49%",fig.ncol = 2, fig.subcap=c('', '', ''), fig.show='hold', fig.align='left'}
     knitr::include_graphics(c(here::here("figures", "envTrend7Totba.png"),
                              here::here("figures", "envTrend7WB.png"),
                              here::here("figures", "envTrend7DDS.png")))
```

>>>>

---
title: "Supplementary figures\nCapturing regeneration in models of forest dynamics"
author: 
- Olalla Díaz-Yáñez, 
- Yannek Käber, 
- Mats Mahnken, 
- Samuel Fischer, 
- Xavier Morin, 
- Manfred Lexer, 
- Christian Hochauer, 
- Katarina Merganicova, 
- Tobias Mette, 
- Werner Rammer, 
- Kristin H. Braziunas, 
- Paola Mairota, 
- Josef Bruna,
- Heike Lischke, 
- Daniel Scherrer, 
- Simon Scheiter, 
- Thomas Hickler, 
- Tim Anders,
- Jessica Hetzer, 
- Harald Bugmann
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float", "subfig"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: global-change-biology.csl
editor_options: 
  markdown: 
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

```{r nvTrend710, echo=FALSE, fig.cap="Mean ingrowth values across the 200 samples per site, for the 200 sites against gradients of (a) total basal area; (b) climatic water balance; (c) seasonal degree sum. The values were split into ten bins; the red lines represent a GAM model showing the trend in the observed data.", fig.show = 'hold', out.width="49%",fig.ncol = 2, fig.subcap=c('', '', ''), fig.show='hold', fig.align='left'}
   knitr::include_graphics(c(here::here("figures", "envTrend7Totba_500.png"),
                              here::here("figures", "envTrend7WB_500.png"),
                              here::here("figures", "envTrend7DDS_500.png")))
```
